%% Seth Li — Curriculum Vitae
%% Source file — edit here, compile with pdflatex, output goes to static/cv/seth_li_cv.pdf
%% Last updated: March 2026

\documentclass[11pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[margin=1in, top=0.80in, bottom=0.80in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

% ── Colors & spacing ──────────────────────────────────────────────────────────
\definecolor{headcolor}{RGB}{17, 87, 64}   % W&M Forest Green

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ── Section heading ───────────────────────────────────────────────────────────
\newcommand{\cvsection}[1]{%
  \vspace{14pt}%
  {\large\bfseries\color{headcolor}\MakeUppercase{#1}}%
  \vspace{2pt}\hrule\vspace{6pt}%
}

% ── Subsection (institution / role group) ─────────────────────────────────────
\newcommand{\cvsubsection}[2]{%
  \vspace{4pt}%
  {\bfseries #1}\hfill{\small #2}\\[-2pt]%
}

% ── Sub-block heading within a section (e.g. Associate Editor, Editorial Board)
\newcommand{\cvsubblock}[1]{%
  \vspace{7pt}%
  {\bfseries #1}\\[-2pt]%
}

% ── Publication list: numbered ────────────────────────────────────────────────
\newlist{publist}{enumerate}{1}
\setlist[publist]{
  label=\arabic*.,
  leftmargin=*,
  itemsep=4pt,
  parsep=0pt,
  topsep=2pt,
}

% ── Simple numbered list ──────────────────────────────────────────────────────
\newlist{cvlist}{enumerate}{1}
\setlist[cvlist]{
  label=\arabic*.,
  leftmargin=*,
  itemsep=3pt,
  parsep=0pt,
  topsep=2pt,
}

% ── Teaching row: course + stats on one line ──────────────────────────────────
\newcommand{\course}[3]{%
  \hspace{1.5em}#1\hfill{\small #2 \textbar\ Avg.\ eval:\ #3}\\[1pt]%
}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\pagestyle{empty}

% ── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{22}{26}\selectfont\bfseries Siyuan (Seth) Li}\\[4pt]
  {\large Dorman Family Distinguished Associate Professor}\\[2pt]
  Raymond A.\ Mason School of Business, William \& Mary\\[5pt]
  {\small 101 Ukrop Way, Williamsburg, VA 23185}\\[2pt]
  {\small
    \href{mailto:seth.li@mason.wm.edu}{seth.li@mason.wm.edu}
    \quad|\quad
    \href{https://www.sethli.net}{www.sethli.net}
    \quad|\quad
    \href{https://orcid.org/0000-0002-0336-9220}{ORCID: 0000-0002-0336-9220}
  }
\end{center}

% ── Academic Positions ────────────────────────────────────────────────────────
\cvsection{Academic Positions}

\cvsubsection{Raymond A.\ Mason School of Business, William \& Mary}{}
\hspace{1.5em}Dorman Family Distinguished Associate Professor \hfill 2024--Present\\
\hspace{1.5em}Assistant Professor \hfill 2018--2024\\[4pt]

\cvsubsection{College of Business, Clemson University}{}
\hspace{1.5em}Assistant Professor \hfill 2014--2018\\
\hspace{1.5em}Visiting Assistant Professor \hfill 2013--2014\\

% ── Education ─────────────────────────────────────────────────────────────────
\cvsection{Education}

\cvsubsection{Terry College of Business, The University of Georgia}{Athens, GA}
\hspace{1.5em}Ph.D.\ in Management Information Systems \hfill 2008--2013\\
\hspace{1.5em}{\small Advisor: Dr.\ Elena Karahanna}\\[4pt]

\cvsubsection{Business School, Hong Kong University of Science and Technology}{Hong Kong}
\hspace{1.5em}B.B.A.\ in Management Information Systems and Finance \hfill 2002--2006\\
\hspace{1.5em}{\small First Class Honors}\\

% ── Journal Publications ──────────────────────────────────────────────────────
\cvsection{Journal Publications}

{\small\textit{FT50 = Top 50 Journals per Financial Times Research Ranking; IF = Five-Year Impact Factor}}

\vspace{4pt}
\begin{publist}
  \item Sun, H., Li, S., Tseng, S., \& Peterson, M. (2025). Virtual Reality, Mental Models, and Mindful Decision-Making. \textit{Journal of the Association for Information Systems}, 26(4), 1166--1196. (IF:~7.4)

  \item London, J., Li, S., \& Sun, H. (2022). Seems Legit: An Investigation of the Assessing and Sharing of Unverifiable Messages on Online Social Networks. \textit{Information Systems Research}, 33(3), 978--1001. (\textbf{FT50}; IF:~9.2)

  \item Li, S., Qu, T., \& Yu, Y. (2022). Outside Director Social Network Centrality and Turnover Before Stock Performance Crash: A Friend in Need? \textit{Journal of Corporate Finance}, 76, Article 102280. (IF:~5.9)

  \item Deng, H., Wang, W., Li, S., \& Lim, K. (2022). Can Positive Online Social Cues Always Reduce User Avoidance of Sponsored Search Results? \textit{MIS Quarterly}, 46(1). (\textbf{FT50}; IF:~11.0)

  \item Pu, W., Li, S., Bott, G., Esposito, M., \& Thatcher, J. (2022). To Disclose or Not to Disclose: An Evaluation of the Effects of Information Control and Social Network Transparency. \textit{Computers \& Security}, 112. (IF:~5.4)

  \item Scott, K., Zagenczyk, T., Li, S., Gardner, W., Cogliser, C., \& Laverie, D. (2018). Social Network Ties and Organizational Citizenship Behavior: Evidence of A Curvilinear Relationship. \textit{European Journal of Work and Organizational Psychology}, 27(6), 752--763. (IF:~5.7)

  \item Li, S., \& Karahanna, E. (2015). Online Recommendation Systems in a B2C E-Commerce Context: A Review and Future Directions. \textit{Journal of the Association for Information Systems}, 16(2). (IF:~7.4)

  \item Li, S., Boudreau, M., Huber, M., \& Watson, R. (2013). Sustainability Performance and CSR Disclosure: The Missing Link. \textit{International Journal of Social Ecology \& Sustainable Development}, 4(2).

  \item Watson, R., Boudreau, M., Li, S., \& Levis, J. (2010). Telematics at UPS: En Route to Energy Informatics. \textit{MIS Quarterly Executive}, 9(1).
  {\small\\\hspace{1.5em}\textit{Best Paper Award} (1st Place, SIM Best Paper Award Competition,~2009)}
\end{publist}

% ── Working Papers ────────────────────────────────────────────────────────────
\cvsection{Working Papers}

\begin{publist}
  \item Li, S., Sun, H., Zhao, Q., \& Wang, Y. ``I Go For That Offbeat Option! Examining Contrarian Behavior in Online Marketplaces.'' Under 4th-round review, \textit{MIS Quarterly}.

  \item Zhao, E., Shea, C., \& Li, S. ``How Pre-existing Relationships between New Team Members Affect Individual and Team Performance.'' Under 2nd-round R\&R, \textit{Organization Science}.

  \item Li, S., Sun, H., Wang, W., \& Zou, H. ``To Follow or Not to Follow? Examining Online Herd Cues' Effect on Herd Behavior.'' Under 2nd-round R\&R, \textit{Journal of the Association for Information Systems}.

  \item Wang, Y., Zhao, Q., \& Li, S. ``To Craft or Not to Craft? The Impact of Algorithmic Knowledge on Creators' Creative Behavior.'' Under review, \textit{Information Technology and People}.

  \item Li, S.\ \& Kohli, R. ``Bridging the Social Divide: How Generative AI Can Foster Understanding and Reduce Polarization.'' Work-in-progress.
\end{publist}

% ── Presentations ─────────────────────────────────────────────────────────────
\cvsection{Presentations and Conference Proceedings}

\begin{publist}
  \item Li, S.\ \& Kohli, R. (2026). ``Information Systems and Social Divide: How Large Language Models Moderate Polarization.'' Virginia Research Seminar Series, George Mason University.

  \item Zhao, E., Shea, C., \& Li, S. (2026). ``Shared Histories in New Teams: The Effect of Pre-Existing Relationships on Performance.'' IACM 2026, Vienna, Austria.

  \item Li, S.\ \& Kohli, R. (2025). ``Bridging the Social Divide: How Generative AI Can Foster Understanding and Reduce Polarization.'' Brownbag Series, Mason School of Business, William \& Mary.

  \item Zhao, E., Shea, C., \& Li, S. (2024). ``How Pre-existing Relationships between New Team Members Affect Individual and Team Performance.'' IACM 2024, Singapore.

  \item Li, S., Shen, R., \& Yu, Y. (2023). ``Does Corporate ESG Disclosure Spillover Through Board Interlocks?'' Brownbag Series, Mason School of Business, William \& Mary.

  \item Shea, C., Li, S., \& Zhao, E. (2022). ``Familiar Faces in New Places: How Pre-existing Relationships between New Team Members Affect Individual and Team Performance.'' 82nd Annual Meeting of the Academy of Management, Seattle, WA (Showcase Symposium).

  \item Kohli, R.\ \& Li, S. (2021). ``Economic Rationality and Strategy: How Institutional Logics Explain ACO's Pursuit of Healthcare Cost-savings.'' Brownbag Series, Mason School of Business, William \& Mary.

  \item Kohli, R.\ \& Li, S. (2021). ``Learning to be Rational: Economic Rationality among Accountable Care Organizations.'' Virginia Research Seminar Series, George Mason University.

  \item Jia, L.\ \& Li, S. (2020). ``Peer Effects on Knowledge Contribution Behaviors.'' 2020 INFORMS Annual Meeting, Virtual.

  \item Tofangchi, S., Hanelt, A., \& Li, S. (2019). ``Advancing Recommendations on Two-Sided Platforms: A Machine Learning Approach to Context-Aware Profiling.'' ICIS 2019, Munich, Germany.

  \item Li, S.\ \& Sun, H. (2019). ``Herd Booster: Examine the Impact of Product and Recommendation Type on Herd Behavior.'' SIG-DIGIT, ICIS 2019, Munich, Germany.

  \item Wade, J., Li, S., Pu, W., \& Thatcher, J. (2018). ``Turning the Negative Affiliation Around: Looking Glass Self in Online Community Platforms.'' ICIS 2018, San Francisco, CA.

  \item Purvis, R.\ \& Li, S. (2018). ``The Development of Psychological Climate within IS Development Projects and Its Impact on IS Development Project Performance.'' ECIS 2018, Portsmouth, UK.

  \item Scott, K., Zagenczyk, T., Li, S., Gardner, W., Cogliser, C., \& Laverie, D. (2017). ``Citizenship Behavior of Included and Excluded Employees: Evidence of a Curvilinear Relationship.'' 77th Annual Meeting of the Academy of Management, Atlanta, GA (\textit{Best Accepted Paper}).

  \item Pu, W., Li, S., \& Thatcher, J. (2017). ``Self-disclosure and SNS Platforms: The Impact of SNS Transparency.'' ICIS 2017, Seoul, South Korea.

  \item Scott, K., Zagenczyk, T., \& Li, S. (2017). ``Social Network Ties and Organizational Citizenship Behavior: A Social Network Analysis.'' 32nd Annual Conference of the SIOP, Orlando, FL.

  \item Pu, W., Li, S., \& Thatcher, J. (2016). ``Self-disclosure and SNS Platforms: The Impact of SNS Transparency and Culture.'' SIG-DIGIT, ICIS 2016, Dublin, Ireland.

  \item Pu, W., Li, S., \& Thatcher, J. (2016). ``Self-disclosure and SNS Platforms: The Impact of Transparency, Accountability, and Culture.'' AMCIS 2016, San Diego, CA.

  \item Li, S.\ \& Sun, H. (2015). ``The Role of System Type in Herd Behavior in User Adoption and Continuance of Technology.'' ICIS 2015, Fort Worth, TX.

  \item Li, S.\ \& Karahanna, E. (2012). ``Peer-based Recommendations in Online B2C E-Commerce: Comparing Collaborative Personalization and Social Network-based Personalization.'' HICSS 2012, Maui, HI.

  \item Li, S., Boudreau, M., \& Watson, R. (2011). ``Why Organizations Have Different Levels of Sustainability Disclosure: A Study of CSR Quality in the IT Industry.'' 54th ASAC, Montr\'{e}al, QC, Canada.

  \item Watson, R., Williamson, T., Boudreau, M., \& Li, S. (2011). ``Business Canvas for Energy Informatics.'' SIG Green, ICIS 2011, Saint Louis, MO.
\end{publist}

% ── Teaching ──────────────────────────────────────────────────────────────────
\cvsection{Teaching Experience}

\cvsubsection{William \& Mary}{2018--Present}
\course{BUAD467 Predictive Analytics (BBA)}{2 sections}{in progress}
\course{BUAD466 Developing Business Intelligence (BBA)}{3 sections}{4.48/5}
\course{BUAD5762 Business Analytics Capstone (MSBA, OMSBA)}{2 sections}{4.75/5}
\course{BUAD5732 Data Visualization (MSBA)}{6 sections}{4.75/5}
\course{BUAD6271 Data Management (FT-MBA, PT-MBA, OMSBA)}{8 sections}{4.88/5}
\course{BUAD6971 MBA Independent Studies (MBA)}{1 section}{5.00/5}

\vspace{4pt}
\cvsubsection{Clemson University}{2013--2018}
\course{MGT3500 Introduction to Business Analytics (BBA)}{7 sections}{4.32/5}
\course{MGT4560 Business Data Management (BBA)}{8 sections}{4.40/5}
\course{MGT8990 PhD Independent Studies}{1 section}{5.00/5}

\vspace{4pt}
\cvsubsection{University of Georgia}{2010--2013}
\course{MIST4600 Computer Programming in Business (BBA)}{2 sections}{4.3/5}
\course{MIST4620 System Analysis and Design (BBA)}{4 sections}{4.5/5}
\course{MIST5620 Business Intelligence (BBA)}{1 section}{4.3/5}

% ── Research Grants ───────────────────────────────────────────────────────────
\cvsection{Research Grants}

\begin{publist}
  \item Li, S.\ \& Kohli, R. (2024). AI Initiatives Grant, Raymond A.\ Mason School of Business, William \& Mary. Award: \$4,000.

  \item Li, S. (2021--2024). Summer Research Grant, Raymond A.\ Mason School of Business, William \& Mary. Award: \$20,000/year.

  \item Li, S., Qu, T., \& Yu, Y. (2014). ``Outsider Information for Insider Trading: A Social Network Analysis.'' Singapore Ministry of Education, Tier 1 Grant (MOE2014-T1-001-240). Award: S\$79,960 (${\sim}$US\$64,000). Competitively reviewed national external grant.
\end{publist}

% ── Professional Services ─────────────────────────────────────────────────────
\cvsection{Professional Services --- External}

\cvsubblock{Associate Editor}
\begin{cvlist}
  \item MIS Quarterly,~2026--present
  \item Journal of the Association for Information Systems,~2026--present
  \item Decision Support Systems,~2025--present
\end{cvlist}

\cvsubblock{Editorial Board}
\begin{cvlist}
  \item AIS Transactions on Human-Computer Interaction (THCI),~2025--present
  \item Journal of the Association for Information Systems,~2024--2026
\end{cvlist}

\cvsubblock{Mini Track Chair}
\begin{cvlist}
  \item Global Development Track. Americas Conference on Information Systems, Virtual,~2020
  \item Global Development Track. Americas Conference on Information Systems, Canc\'{u}n, Mexico,~2019
  \item ICTs in Global Development Track. Americas Conference on Information Systems, New Orleans,~2018
\end{cvlist}

\cvsubblock{Conference Associate Editor}
\begin{cvlist}
  \item IS Innovation, Adoption and Diffusion Track. ECIS, Milan, Italy,~2026
  \item IS Innovation, Adoption and Diffusion Track. ECIS, Amman, Jordan,~2025
  \item IT Implementation and Adoption Track. ICIS, Bangkok, Thailand,~2024
  \item IS Innovation, Adoption and Diffusion Track. ECIS, Paphos, Cyprus,~2024
  \item Social Impact of IS Track. ICIS, Hyderabad, India,~2023
  \item Governance, Strategy and Value of IS Track. ICIS, Virtual,~2020
  \item Cognition and Human Behavior in IS Track. ECIS, Marrakech, Morocco,~2020
  \item Human Computer Interaction Track. PACIS, Dubai, UAE,~2020
  \item Human Behavior and IS Track. ICIS, Munich, Germany,~2019
  \item Cognition and Human Behavior in IS Track. ECIS, Stockholm, Sweden,~2019
  \item Human Behavior and IS Track. ICIS, San Francisco, CA,~2018
  \item Human Behavior and IS Track. ICIS, Seoul, South Korea,~2017
  \item Sustainability and Societal Impacts of IS Track. ICIS, Dublin, Ireland,~2016
  \item E-Business and E-Government Track. PACIS, Chiayi, Taiwan,~2016
  \item Sustainability and Societal Impacts of IS Track. ICIS, Fort Worth, TX,~2015
\end{cvlist}

\cvsubblock{Session Chair}
\begin{cvlist}
  \item Human Computer Interaction Track. ICIS, Bangkok, Thailand,~2024
  \item IT Implementation Track. ICIS, India (virtual),~2020
  \item Human Behavior and IS Track. ICIS, Seoul, South Korea,~2017
  \item IS Adoption and Diffusion Session. PACIS, Singapore,~2015
  \item Evolution and Appropriation in IS Perceptions and Utilization II Session. ICIS, Auckland, New Zealand,~2014
\end{cvlist}

\cvsubblock{Reviewer}
\begin{cvlist}
  \item \textit{Journals:} MIS Quarterly, Information Systems Research, Journal of Management Information Systems, Journal of the Association for Information Systems, Journal of Strategic Information Systems, Information \& Management, Information Systems Journal, Information Systems Frontiers, Information Technology \& People, Internet Research, Journal of Industrial Ecology, Database, Decision Science, Decision Support Systems
  \item \textit{Conferences:} ICIS, AMCIS, ECIS, HICSS, PACIS
\end{cvlist}

\cvsection{Professional Services --- Internal}

\cvsubblock{Service at William \& Mary}
\begin{cvlist}
  \item Research Brownbag Series Coordinator,~2023--2024
  \item Research Committee, Mason School of Business,~2022--2024
  \item Business Research Subject Participation System (SONA) Coordinator,~2021--2022,~2025--present
  \item First-Year Undergraduate Student Advisor,~2019--2023
  \item Faculty Search Committee,~2019,~2020,~2022
  \item Research Digest Editor,~2020
  \item Independent Study Advisor,~2020
\end{cvlist}

\cvsubblock{Service at Clemson University}
\begin{cvlist}
  \item Business Analytics Curriculum Developer for Undergraduate and Graduate Programs,~2014--2016
  \item Consultant, AIS SAP Competition, University of Indiana,~2016
  \item Case Leader, CoMIS Case Competition, University of Minnesota,~2015
  \item PhD Dissertation Committee,~2016--2018
  \item Faculty Search Committee,~2014--2017
  \item PhD Recruitment Committee,~2015--2017
  \item Research Workshop Coordinator,~2014
\end{cvlist}

% ── Awards ────────────────────────────────────────────────────────────────────
\cvsection{Academic Awards and Honors}

\begin{cvlist}
  \item Best Reviewer of The Year (2024), Journal of the Association for Information Systems
  \item Best Reviewer Award (2023), AIS Transactions on Human-Computer Interaction
  \item Dean's Research Fellow (2021--2025), Mason School of Business, William \& Mary
  \item Best Accepted Paper (2017), 77th Annual Meeting of the Academy of Management, Atlanta, GA
  \item Doctoral Teaching Award for Outstanding Teaching (2013), Department of MIS, University of Georgia
  \item 1st Place, SIM Best Paper Award Competition (2009), Society for Information Management
  \item Influencer on a Class of 2020 Graduate, Cohen Career Center, William \& Mary
  \item Etheredge Scholarship (2008--2011), Terry College of Business, University of Georgia
\end{cvlist}

% ── Additional Training ───────────────────────────────────────────────────────
\cvsection{Additional Training}

Completion Certificate, Social Network Analysis Training Workshop, LINKS Center, University of Kentucky, July 5--10,~2011

% ── Memberships ───────────────────────────────────────────────────────────────
\cvsection{Professional Memberships}

Association for Information Systems (AIS)\\
AIS Special Interest Group on Adoption and Diffusion of Information Technology (SIGADIT)\\
AIS Special Interest Group on Human Computer Interactions (SIGHCI)

\end{document}
